\documentclass{resume}

\renewcommand{\categoryfont}{\sc}

%
% set the space used for category titles here:
% use the same value for oddsidemargin and marginparwidth [the latter 
% 		will be reset to account for marginparsep]
% 
\setlength{\oddsidemargin}{1in}
\setlength{\marginparwidth}{1in}
% 
% calculate other dimensions [textwidth and evensidemargin] 
% in function of oddsidemargin and marginparwidth: 
% would be nicer to put in the class file...
%
\addtolength{\marginparwidth}{-\marginparsep}
 \setlength{\evensidemargin}{\oddsidemargin}
 \setlength{\textwidth}{\paperwidth}
 \addtolength{\textwidth}{-2in}
 \addtolength{\textwidth}{-2\oddsidemargin}
 \addtolength{\textwidth}{\marginparwidth}
 \addtolength{\textwidth}{\marginparsep}
%
%
\setlength{\topmargin}{-0.5in}
%
%
\renewcommand{\labelcitem}{$\diamond$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }

\author{Babin Babu}
% ------ Address --------------------------------------------------------

\address{Software Engineer\\
  DXC Technology\\
  Persiaran Rimba Permai\\
  Cyberjaya, Malaysia\\
  {\em Ph:} (+60)-16-731-6496 (MY)\\
  {\em Ph:} (+91)-94-4679-6340 (IN)}{
  {\em email:} \mbox{\small\tt mail@iambabin.com}\\
  {\em web:} \mbox{\small\tt www.iambabin.com}\\
  {\em github:} \mbox{\small\tt github.com/babinbabu}\\
  {\em linkedin:} \mbox{\small\tt linkedin.com/in/babinbabu}\\
  }

\begin{document}
\maketitle

% ------- Education ---------------------------------------------------

\begin{category}{Education}
  \citem{Master’s Degree, MCA} 
  \hfill \textbf{2010 -- 2013}
  \citemnobullet Amal Jyothi Engineering College, Kanjirappally, Kerala, India.
  \citem{Degree, Mathematics}
  \hfill \textbf{2007 -- 2010}
  \citemnobullet CMS College Kottayam, Kerala, India.
  \citem{HSE in Computer Science} 
  \hfill \textbf{2005 -- 2007}
  \citemnobullet St. Joseph HSS Paingottoor, Kerala, India.
\end{category}

% --------- Research ----------------------------------------------------

\begin{category}{Research interests}
  \citemnobullet MuleSoft, XMPP Server,Testing Tool creation, Wordpress Plugins, Test Driven Developinterests ment, Design Patterns, Clean Code.
\end{category}

\begin{category}{Technical Skills}
  \citembullet {\it Operating Systems}: GNU/Linux, Mac OSX, Microsoft Windows.
  \citembullet {\it Programming Languages}: C\#, VB.NET, PHP, Java Script, HTML5, CSS3.Objective C, .NET.
  \citembullet {\it Frameworks}: ASP.NET, .Net Core, ASP MVC, Umbraco, jQuery, Angular Js.
  \citembullet {\it Databases}: MySQL, SQL Server, Oracle
  \citembullet {\it Tools}:  Jenkins, Jira
  \citembullet {\it Version Control}: Git, SVN, TFS
  \citembullet {\it Cloud Platforms}:Azure, Google App Engine, Amazon.
  \citembullet {\it Specialities}: Web services, Automation \& deployment, Web application development, Test Driven Development, experienced in Agile software development methodologies, full stack developer.
\end{category}

% -------- Work experience --------------------------------------------

\begin{category}{Work \\experience}
  \citem{DXC Technology, Cyberjaya - Malaysia}
  \citemnobullet \textbf{Software  Engineer} \hfill \textbf{July  2019 -- present}
  \citemnobullet DXC Technology is the world’s leading independent, end-to-end IT services and solutions company, helping customers harness the power of innovation to thrive on change.
  \begin{itemize}
  \item \textbf{CMS APP} {\em July 2019 - present}: Its a Card Management system which uses many banks in US {\em ASP.NET,JQUERY, HTML, CSS, IIS Server,Oracle}. \textbf{Role}: {\em Developer}. 
  \end{itemize}
  \citem{Cardtrend Systems Sdn Bhd, 1 Tech Park - Malaysia}
  \citemnobullet \textbf{Software Engineer} \hfill \textbf{March 2017 – July 2019}
  \citemnobullet Founded in 2001 and based in Kuala Lumpur (Malaysia); we are specialized in end-to-end close-loop payment and loyalty solutions. With our team of industry specialists we aim to deliver innovative and high quality services to our clients and stakeholders, along with unmatched security and resilience
  \begin{itemize}
  \item \textbf{Metro Oil} {\em March 2017 – July 2019}:Its a cardless loyalty system for customers. Customers Smart Phone App will be the virtual card, Its have a lot featurs like promotion, referals and claim voucher etc {\em  .Net Core,Web Api,Angular JS, MVC, HTML5, SQL Server}. \textbf{Role}: {\em Developer}. 
  \item \textbf{Petronas} {\em March 2017 – July 2019}: : Ticket Fleet is a web based Card Management System
developed by Cardtrend Systems Sdn Bhd. Ticket Fleet is customized specifically
for Petronas to handle fleet cards for their customers. {\em ASP.Net,Angular JS, MVC, HTML5, SQL Server. }. \textbf{Role}: {\em Developer}. 
  \item \textbf{Petron} {\em March 2017 – July 2019}: Ticket Fleet is a web based Card Management System developed by Cardtrend Systems Sdn Bhd. Ticket Fleet is customized specifically for Petronas to handle fleet cards for their customers. {\em ASP.Net,Angular JS, MVC,HTML5, SQL Server}. \textbf{Role}: {\em Developer}. 
  \end{itemize}
  \citem{Agmo Studio Sdn Bhd, Malaysia (On site from Polus Software) - Polus Software }
  \citemnobullet \textbf{Software Engineer} \hfill \textbf{October 2015 -- February 2017}
  \citemnobullet Agmo Studio is a Malaysia mobile applications development company that develop apps for several platform include iOS and Android. Malaysia premier apps developer that develop apps for iPhone, iPad, iPod Touch, iOS, Android located at Kuala Lumpur, Malaysia.
  \begin{itemize}
  \item \textbf{Makan2U App} {\em Feb 2016 - Feb 2017:}:This app to keep in touch faster, easier and better with the restaurant you eat frequently from. If you are a loyal customer of one of our member-food business, this is the online food ordering app for you {\em ASP MVC, Web API, SQL Server, iOS, Android}. \textbf{Role}: {\em Developer}. 
  \item \textbf{MELAKA Response App} {\em Feb 2016 - Feb 2017}: : Melaka Response is a new invention of mobile application made by Melaka State Government under citizen engagement initiative. This application allows the people of Melaka to communicate with various government agencies and authorities and later interactively get response back within
  the application.  {\em Ruby on Rails and MySQL}. \textbf{Role}:{\em Developer}.

  \item \textbf{Next Property App} {\em Feb 2016 - Feb 2017}: NextProperty App is the 1st ever Malaysian new property app that maps out all transportation rail lines. With the upcoming MRT, LRT Extension and existing rail lines like the KTM Komuter, LRT, Monorail and such around your property, you can be assured of high yield and utmost convenience. {\em ASP, MVC, Web API, SQL Server, iOS, Android}. \textbf{Role}: {\em Developer}.
  \end{itemize}
  \citem{CYBOSOL Infotech (Nuevalgo Solutions), Technopark Trivandrum, India} 
  \citemnobullet \textbf{Software Engineer} \hfill \textbf{March 2014 – Sept 2015}
  \citemnobullet Nuevalgo is a product and services company who delivers custom software for desktop, web,mobile and cloud-based environments.
  \begin{itemize} 
  \item \textbf{Bakeeth} {\em Oct 2014 - Jan 2015}: Its a CMS based web application using {\em C\#.NET,Umbraco,SQL Server}. \textbf{Role}: {\em Programmer}.
  \item \textbf{AUFGC Vendor Portal}: Web based Business application and Multi Level Marketing
    application using {\em ASP.NET, C\#.NET and MS SQL}. \textbf{Role}: {\em Programmer}.
  \item Standalone application for a Business System using {\em C\#.NET and MS SQL}.
  \end{itemize}
\end{category}

% -------- Awards & Honours ---------------------------------------

\begin{category}{Awards \&\\ Honours}
  \citem{``Attended jQuery conference''}, {\em
    Chancery Pavilion Hotel Bangalore}. \hfill \textbf{2014}
  \citem{``Part of the event Best Techies of AZURE12''}, {\em national level techno-cultural-managerial Honours Festival held at Amal Jyothi College of Engineering }. \hfill \textbf{2013}
  \citem{``Attended UGC-sponsored national conference on Green Computing''} {\em , Marian College, Kuttikkanam}. \hfill \textbf{2011}
\end{category}


% -------- Personal Profile --------------------------------------------
\begin{category}{Personal Profile}
 
\citembullet {\it Date of Birth}           :   25/08/1989 
\citembullet {\it Nationality}             :   Indian 
\citembullet {\it Gender}                  :   Male 
\citembullet {\it Age}                     :   31 Years 
\citembullet {\it Marital Status}          :   Married 
\citembullet {\it Father’s Name}           :   Babu K John 
\citembullet {\it Mother’s Name}           :   Mollykutty Babu 
\citembullet {\it Passport Number}         :   K3891967
\citembullet {\it Willing to Relocate}     :   Yes
\end{category}



% -------- Reference --------------------------------------------

\begin{category}{Reference}
  \citemnobullet \\
  \begin{tabular}{ll}Shihabudheen P K& LEE Khar Yeong\\
    CEO& Project Portfolio Manager\\
    Winwius Techno Solutions&Cardtrend Systems Sdn Bhd\\
    Infopark, Kochi, Kerala& Bandar Utama, Malaysia\\
    Email: \mbox{\small\tt shihabudheen.pk@gmail.com}&Email: \mbox{\small\tt kharyeong@cardtrend.com}\\
    Ph: (+91)-99-6142-9066&Ph: (+60)-18-575-1198
  \end{tabular}
\end{category}
\end{document}
